### 2023-04-27 paper.Rmd
minor editing

[^dissimilarityfromfeatures]: It is still possible to convert the attribute data into a dissimilarity matrix, e.g. by computing all pairwise Euclidean distances, and then optimize a distance-based anticlustering criterion to obtain a partitioning. For likert scale data or binary attributes, the Manhattan distance may be preferred over the Euclidean distance, and for mixed-type attributes, it is even possible to employ a combined distance metric [@rokach2005].

@@

As a last outlook, it should be noted that because the covariance is defined as an expected value, the k-plus logic can be extended to minimize differences with regard to covariances, a possibility that was not investigated in the current paper. The covariance between two variables $x = (x_1, \ldots, x_N)$ and $y = (y_1, \ldots, y_N)$ is defined as $\frac{1}{N} \sum\limits_{i=1}^{N} (x_i - \overline{\mathbf{x}}) (y_i -\overline{\mathbf{y}})$. Thus, to maximize between-group similarity with regard to covariance structure, it is possible to augment the data set with an additional variable for each pair of variables $x$ and $y$, computed as $(x_i - \overline{\mathbf{x}}) (y_i -\overline{\mathbf{y}})$. Future research should examine how the k-plus approach can be adapted to including covariances, including a discussion of how to select weights for the possibly high number of additional variables. The unweighted standardization approach presented here may serve as a starting point for investigation.

>>>>

[^dissimilarityfromfeatures]: It is still possible to convert the attribute data into a dissimilarity matrix, e.g. by computing all pairwise Euclidean distances, and then optimize a distance-based anticlustering criterion to obtain a partitioning. For likert scale data or binary attributes, the Manhattan distance may be preferred over the Euclidean distance; for mixed-type attributes, it is even possible to employ a combined distance metric [@rokach2005].

@@

As an additional outlook, it should be noted that because the covariance is defined as an expected value, the k-plus logic can be extended to minimize differences with regard to covariances, a possibility that was not investigated in the current paper. In this case, an additional variable has to be computed for each pair of variables $x = (x_1, \dots, x_N)$ and $y = (y_1, \dots, y_N)$, computed as $(x_i - \overline{\mathbf{x}}) (y_i -\overline{\mathbf{y}})$. Future research should examine how the k-plus approach can be adapted to including covariances. The unweighted standardization approach presented here may serve as a starting point for investigation.
